---
title: "Pregnancy Episode Analysis Report"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
```

# Introduction

This report presents the analysis of pregnancy episodes identified from the dataset. The analysis includes:
- Complex episode identification
- Validation of episodes
- Confidence scoring
- Quality control assessment

# Data Overview

```{r data_overview}
# Load results
results <- readRDS("analysis_results.rds")

# Display summary statistics
kable(results$quality_report$summary_stats, 
      caption = "Summary Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Episode Distribution

```{r episode_distribution}
# Display episode date distribution plot
results$quality_report$plots[[1]]
```

# Confidence Score Distribution

```{r confidence_distribution}
# Display confidence score distribution plot
results$quality_report$plots[[2]]
```

# Validation Results

```{r validation_results}
# Display validation results
kable(results$validation_results, 
      caption = "Episode Validation Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Confidence Scores

```{r confidence_scores}
# Display confidence scores
kable(results$confidence_scores, 
      caption = "Episode Confidence Scores") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Quality Control Assessment

```{r quality_assessment}
# Add quality control assessment here
# This section will be populated based on the quality control results
```

# Conclusions

```{r conclusions}
# Add conclusions here
# This section will be populated based on the analysis results
``` 