---
title: "Pregnancy Episode Analysis Report"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)

# Set working directory to workspace root
setwd(here::here())
```

# Introduction

This report presents the analysis of pregnancy episodes identified from the dataset.

# Data Overview

```{r load-data}
# Load the analysis results
results <- readRDS(here::here("output", "analysis_results.rds"))

# Convert to a more readable format
episodes_summary <- results %>%
  unnest(cols = c(start_date, end_date)) %>%
  mutate(
    duration = as.numeric(difftime(end_date, start_date, units = "days")),
    duration_weeks = round(duration / 7, 1)
  )
```

## Summary Statistics

```{r summary-stats}
# Calculate summary statistics
summary_stats <- episodes_summary %>%
  summarise(
    n_episodes = n(),
    mean_duration = mean(duration_weeks, na.rm = TRUE),
    median_duration = median(duration_weeks, na.rm = TRUE),
    min_duration = min(duration_weeks, na.rm = TRUE),
    max_duration = max(duration_weeks, na.rm = TRUE)
  )

# Display summary statistics
kable(summary_stats, 
      caption = "Summary of Pregnancy Episodes",
      digits = 1) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Duration Distribution

```{r duration-plot}
# Create histogram of episode durations
ggplot(episodes_summary, aes(x = duration_weeks)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "white") +
  labs(
    title = "Distribution of Pregnancy Episode Durations",
    x = "Duration (weeks)",
    y = "Count"
  ) +
  theme_minimal()
```

# Validation Results

```{r validation-results}
# Extract and summarize validation results
validation_summary <- results %>%
  select(patient_id, validation_results) %>%
  unnest(validation_results) %>%
  mutate(
    has_temporal_issues = map_lgl(temporal, ~length(.) > 0),
    has_clinical_issues = map_lgl(clinical, ~length(.) > 0),
    has_outcome_issues = map_lgl(outcome, ~length(.) > 0)
  ) %>%
  group_by(patient_id) %>%
  summarise(
    has_temporal_issues = any(has_temporal_issues),
    has_clinical_issues = any(has_clinical_issues),
    has_outcome_issues = any(has_outcome_issues)
  )

# Calculate validation statistics
validation_stats <- validation_summary %>%
  summarise(
    n_patients = n(),
    n_temporal_issues = sum(has_temporal_issues),
    n_clinical_issues = sum(has_clinical_issues),
    n_outcome_issues = sum(has_outcome_issues)
  )

# Display validation statistics
kable(validation_stats,
      caption = "Validation Results Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Conclusion

This analysis has identified and validated pregnancy episodes from the dataset. The results show the distribution of episode durations and highlight any potential issues identified during validation.

Key findings:
- Total number of episodes: `r summary_stats$n_episodes`
- Mean episode duration: `r round(summary_stats$mean_duration, 1)` weeks
- Number of episodes with validation issues: `r sum(validation_stats$n_temporal_issues + validation_stats$n_clinical_issues + validation_stats$n_outcome_issues)` 